% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Tuong Le}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {computer science, machine learning, data mining},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  Sejong University \\
  Digital Contents Research Institute \\
  209, Neungdong-ro, Gwangjin-gu \\
  Seoul, Republic of Korea
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (+82) 010-2104-6385 \\
    	   & (+84) ~~09-3818-6385 \\
    Email: & \href{mailto:tuonglecung@gmail.com}{\tt tuonglecung@gmail.com} \\
    Homepage: & \href{https://sites.google.com/view/tuonglecung/}{\tt https://sites.google.com/view/tuonglecung/} \\
  \end{tabular}
\end{minipage}


\section*{EDUCATION}

\begin{itemize}

  \item Ph.D. Digital Contents, Sejong University, Republic of Korea (3/2017--2/2020)

  \item M.S. Computer Science, University of Information Technology, Viet Nam National University Ho Chi Minh City, Vietnam (2011--2014)
  
  \item B.S. Information Technology, University of Science, Viet Nam National University Ho Chi Minh City, Vietnam (2005--2009)

\end{itemize}


\section*{EMPLOYMENT}

\begin{itemize}

\item Research Assistant, Sejong University, Seoul, Korea (2017--now)
\item Researcher, Division of Data Science, Ton Duc Thang University, Vietnam (2014--2017)
\item Lecturer, Faculty of Information Technology, Ho Chi Minh City University of Food Industry, Vietnam (2010-2014)
\item Developer, Innotech Co., Ltd., Vietnam (2009--2010)
\end{itemize}

\section*{RESEARCH INTERESTS}

\begin{itemize}

\item Machine learning, Imbalanced learning
\item Data analysis, Data mining, Pattern mining 

\end{itemize}


\section*{AWARDS AND SCHOLARSHIPS}

\begin{itemize}

\item PhD research fellow (3/2017--2/2020), by IMLab, Sejong University, South Korea 
\item Student Travel Grant, IEEE SMC 2013, Manchester, UK  by NAFOSTED, Vietnam
\item Toshiba scholarship 2012 by Toshiba Co., Ltd
\item Student Travel Grant, IBICA 2012, Kaohsiung, Taiwan by NAFOSTED, Vietnam

\end{itemize}

\section*{RESEARCH PROJECTS}

\begin{enumerate}

\item Building improved classifier on imbalanced financial/business transaction data to predict company bankruptcy. Institute for Information \& communications Technology Promotion (IITP) grant funded by the Korea government (MSIP), Project ID: 2017-0-00506 (Role: Researcher) 

\item Mining patterns and its applications in text clustering and subspace clustering. NAFOSTED, Project ID: 102.05-2015.10, 2015--2017. (Role: Main researcher) 

\item Developing algorithms for mining frequent sequence patterns and rules from sequence databases. NAFOSTED. Project ID: 102.05-2013.20 (2014--2016, Role: Technician)

\item Developing algorithms for mining frequent itemsets and top-k frequent itemsets based on Nodeset structure. FOSTECT, Project ID: FOSTECT.2014.BR.07, 2014--2015. (Role: Researcher) 

\end{enumerate}

\section*{PROFESSIONAL SERVICES}

\subsection*{Invited reviewer for journals}

\begin{enumerate}

\item IEEE Transactions on Cybernetics: 2018
\item Neural Computing and Applications: 2014, 2016, 2017, 2018 (6), \textbf{2019 (2)}
\item IEEE Access: 2016, 2017, 2018 (3), \textbf{2019 (3)}
\item Applied Soft Computing: 2018
\item Engineering Applications of Artificial Intelligence: 2018
\item International Journal of Machine Learning and Cybernetics: 2014, \textbf{2019}
\item Journal of Intelligent and Fuzzy Systems: 2018
\item Journal of Intelligent Information Systems: 2017
\item International Journal of Information Technology \& Decision Making: 2015, 2016
\item Computational Intelligence: 2016
\item Intelligent Automation \& Soft Computing: 2016
\item Progress in Artificial Intelligence (ESCI, Scopus): \textbf{2019}

\end{enumerate}
\subsection*{Invited reviewer for conferences}

\begin{itemize}

\item IJCRS (2018), ACIIDS (2015, 2016), KSE (2014), ICCASA (2013)
\end{itemize}

\subsection*{Paper presentations}

\begin{enumerate}

\item ICNGC 2018, Vung Tau, Vietnam
\item Next Generation Computing Conference 2017, Jeju, Korea
\item ACIIDS 2015, Bali, Indonesia 
\item IEEE SMC 2013, Manchester, UK
\item ACIIDS 2013, Kuala Lumpur, Malaysia
\item IBICA 2012, Kaohsiung, Taiwan
\end{enumerate}

\section*{PUBLICATIONS}

\subsection*{SCI journals}

\begin{enumerate}

\item \textbf{Tuong Le}, Sung Wook Baik. A robust framework for self-care problem identification for children with disability. Symmetry, 11(1), 89, 2019

\item \textbf{Tuong Le}, Bay Vo, Philippe Fournier-Viger, Mi Young Lee, Sung Wook Baik. SPPC: A New Tree Structure for Mining Erasable Patterns in Data Streams. Applied Intelligence, 49(2), 478--495, 2019

\item \textbf{Tuong Le}, Le Hoang Son, Minh Thanh Vo, Mi Young Lee, Sung Wook Baik. A Cluster-Based Boosting Algorithm for Bankruptcy Prediction in a Highly Imbalanced Dataset. Symmetry, 10(7), 250, 2018

\item \textbf{Tuong Le}, Mi Young Lee, Jun Ryeol Park, Sung Wook Baik. Oversampling techniques for bankruptcy prediction: Novel features from a transaction dataset. Symmetry, 10(4), 79, 2018

\item \textbf{Tuong Le}, Bay Vo, Sung Wook Baik. Efficient algorithms for mining top-rank-k erasable patterns using pruning strategies and the subsume concept. Engineering Applications of Artificial Intelligence, 68, 1--9, 2018

\item \textbf{Tuong Le}, Anh Nguyen, Bao Huynh, Bay Vo, Witold Pedrycz. Mining Constrained Inter-Sequence Patterns: A Novel Approach to Cope with Item Constraints. Applied Intelligence, 48(5), 1327--1343, 2018

\item Bay Vo, \textbf{Tuong Le*}, Witold Pedrycz, Giang Nguyen, Sung Wook Baik. Mining erasable itemsets with subset and superset itemset constraints. Expert Systems with Applications, 69, 50--61, 2017

\item Tung Kieu, Bay Vo, \textbf{Tuong Le*}, Zhi-Hong Deng, Bac Le. Mining top-k co-occurrence items with sequential pattern. Expert Systems with Applications, 85, 123--133, 2017

\item Bay Vo, \textbf{Tuong Le*}, Giang Nguyen, Tzung-Pei Hong. Efficient algorithms for mining erasable closed patterns from product datasets. IEEE Access, 5(1), 3111--3120, 2017

\item Bay Vo, Sang Pham, \textbf{Tuong Le*}, Zhi-Hong Deng. A novel approach for mining maximal frequent patterns. Expert Systems with Applications, 73, 178--186, 2017

\item \textbf{Tuong Le}, Bay Vo. The lattice-based approaches for mining association rules: a review. WIREs Data Mining and Knowledge Discovery, 6(2), 140--151, 2016

\item Bay Vo, \textbf{Tuong Le*}, Frans Coenen, Tzung-Pei Hong. Mining frequent itemsets using the N-list and subsume concepts. International Journal of Machine Learning and Cybernetics, 7(2), 253--265, 2016

\item \textbf{Tuong Le}, Bay Vo. An N-list-based algorithm for mining frequent closed patterns. Expert Systems with Applications, 42(19), 6648--6657, 2015

\item Giang Nguyen, \textbf{Tuong Le*}, Bay Vo, Bac Le. EIFDD: An efficient approach for erasable itemset mining of very dense datasets. Applied Intelligence, 43(1), 85--94, 2015 

\item Bay Vo, \textbf{Tuong Le*}, Tzung-Pei Hong, Bac Le. Fast updated frequent-itemset lattice for transaction deletion. Data and Knowledge Engineering, 96–97, 78--89, 2015 

\item Quyen Huynh, \textbf{Tuong Le}, Bay Vo, Bac Le. An efficient and effective algorithm for mining top-rank-k frequent patterns. Expert Systems with Applications, 42(1), 156--164, 2015

\item \textbf{Tuong Le}, Bay Vo, Giang Nguyen. A survey of erasable itemset mining algorithms. WIREs Data Mining and Knowledge Discovery, 4(5), 356--379, 2014

\item Bay Vo, \textbf{Tuong Le}, Tzung-Pei Hong, Bac Le. An effective approach for maintenance of pre-large-based frequent-itemset lattice in incremental mining. Applied Intelligence, 41(3), 759--775, 2014

\item \textbf{Tuong Le}, Bay Vo. MEI: An efficient algorithm for mining erasable itemsets. Engineering Applications of Artificial Intelligence, 27, 155--166, 2014

\end{enumerate}

\subsection*{Peer-reviewed conferences}

\begin{enumerate}

\item Giang Nguyen, \textbf{Tuong Le}, Bay Vo, Bac Le: Discovering Erasable Closed Patterns. ACIIDS 2015, Bali, Indonesia, 368--376

\item Giang Nguyen, \textbf{Tuong Le}, Bay Vo, Bac Le: A New Approach for Mining Top-Rank-k Erasable Itemsets. ACIIDS 2014, Bangkok, Thailand, 73--82

\item Giang Nguyen, \textbf{Tuong Le}, Bay Vo, Bac Le, Phi-Cuong Trinh. Subsume concept in erasable itemset mining. ICCCI 2014, Seoul, Korea, 515--523

\item Bac Le, Bay Vo, Quyen Huynh, \textbf{Tuong Le}. Enhancing the mining top-rank-k frequent patterns. IEEE SMC 2014, San Diego, CA, USA, 2008--2012

\item \textbf{Tuong Le}, Trong Hai Duong, Bay Vo, Sanggil Kang: Consensus for Collaborative Ontology-Based Vietnamese WordNet Building. ACIIDS 2013, Kuala Lumpur, Malaysia, 499--508

\item Bay Vo, \textbf{Tuong Le}, Tzung-Pei Hong, Bac Le: Maintenance of a Frequent-Itemset Lattice Based on Pre-large Concept. KSE 2013, Hanoi, Vietnam, 295--305

\item Bay Vo, \textbf{Tuong Le}, Frans Coenen, Tzung-Pei Hong. A hybrid approach for mining frequent itemsets. IEEE SMC 2013, Manchester, UK, 4647--4651

\item \textbf{Tuong Le}, Bay Vo, Frans Coenen. An efficient algorithm for mining erasable itemsets using the difference of NC-Sets. IEEE SMC 2013, Manchester, UK, 2270--2274

\item \textbf{Tuong Le}, Bay Vo, Trong Hai Duong:
Personalized Facets for Semantic Search Using Linked Open Data with Social Networks. IBICA 2012, Kaohsiung, Taiwan, 312--317

\end{enumerate}

*: Corresponding author

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today 
  \end{footnotesize}
\end{center}

\end{document}
